\noindent
This project has been a true test of what I believe Engineering is - or at least should be - about; a collection of tools that one acquires and develops to solve challenging inter-disciplinary problems in possibly foreign domains. It has thoroughly tested my technical and problem solving skills across several subject areas, including mathematics and statistics, signal processing, electronics, embedded systems programming, web programming and general patience. In addition, through this project, I have learnt about basic neurophysiology and associated neurotechnologies - fields which I was close to clueless about coming in to it. The brain truly is one of nature's most incredible and fascinating machines and this project has inspired me to try understand my own one a little more.
\vspace{0.4cm}

\noindent
My most sincere vote of gratitude goes to the members of the Imperial NGNI Lab. Whether I was in Cape Town, Egypt or London, you managed to meet with me nearly every week since project inception to hear of my progress and more commonly, my trials and tribulations. Your advice and patient guidance was indispensable to me and the success of this project. I am most thankful for your time and wish you every success. \vspace{0.4cm}

\noindent
Finally, I thank my parents and family back home in Cape Town for their endless interest and support in my endeavours. Life in COVID has been challenging to say the least and I am extremely grateful for your help and encouragement. I hope that I have done you proud.